Universal Anonymous Signatures

### 2022-10-04 prism-backend/research/gsac/formal-uas.tex
30 pages.

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all other functions.
\item[$\KeyGen(\parm) \rightarrow (% \Ccom,r,
  \upk,\usk)$.] Given \parm, a user
  runs \KeyGen to generate its user key pair% , and a commitment \Ccom to the
  % public key, with randomness $r$
  . 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\ipk,\sCred,\attrs),
  \Issue(\isk,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk receive a credential
  $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue function defined by the issuer, and $\utrans=(U,I)$ being the
  transcript of the communication% , where $U$ contains the messages sent by
  % the user, and $I$ those sent by the issuer
  .
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving user secret key \usk, opener public key \opk, 
  credentials \sCred, message \msg and evaluation function \feval, returns
  signature \sig, and a value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Run by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials by issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
These are the functional placeholders that allow modulating the behaviour of the
resulting instantiation. They controll the conditions upon which new credentials
can be issued, the information revealed at signing time, or extractable from
signatures. In all cases, the user computes them, and proves correctness of
such computation. We give concrete examples in \secref{sec:relationships}.

@@

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  honest {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  corrupt {\uid}s/{\iid}s/{\oid}s.
\item[\UK,\IK,\OK.] Tables storing key pairs of users $(\upk,\usk)$, issuers
  $(\ipk,\isk)$, and openers $(\opk,\osk)$, indexable by \uid, \iid, and \oid,
  respectively. Issuers' public keys contain a \fissue function, and
  openers' public keys contain a \finsp function.
\item[\PUBUK,\PUBIK,\PUBOK and \PRVUK,\PRVIK,\PRVOK.] Shorthands referring to
  public keys of users, issuers or openers ($\mathsf{PXK}$) or their private
  keys ($\mathsf{SXK}$).
\item[\CRED.] Indexable by \cid, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$) to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but tracks challenge credentials.
\item[\OWNR.] When we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
  $\bot$ if there is no such \uid. We also use \OWNR over a set of {\cid}s
  (\scid). In that case, $\OWNR[\scid]$ returns $\bot$ if
  not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
  \uid, all conditions checking membership of the output of \OWNR to a list of
  users equal false if \OWNR returns $\bot$.
\item[\ATTR.] When we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] When we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

\paragraph{Oracles.} %
In the game-based definitions of our \UAS model, we leverage the following
oracles, which are formally defined in \figref{fig:oracles1} and
\figref{fig:oracles2}.

\begin{description}
% \item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
%   the associated issuance function.
\item[\HUGEN.] Adds a new honest user to the game, generating its keypair.
\item[\CUGEN.] Adds a new corrupt user to the game, setting its \upk to the
  value given by the adversary.  
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting its evaluation and opening functions.
% \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
%   key to the adversary.
\item[\ISET.] ``Upgrades'' a user to become an issuer, specifying its
  \fissue function.
\item[\UCORR.] Corrupts an existing (and honest) user, giving its secret
  key to the adversary. If the user was also an issuer, it becomes a corrupt
  issuer too.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.
% \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
%   the user's key pair.
% \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
%   user already exists and is honest, corrupts it, leaking its key and
%   credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures using credentials from honest
  users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

@@

    \caption{Detailed oracles available in our model (1/2). Oracles for
      generating key material for users, issuers, and openers.}
    \label{fig:oracles1}
  \end{figure*}
}

@@

@@

\paragraph{Helper functions \SimSetup, \ExtractIssue, and \ExtractSign.}
We assume the existence of these helper functions. They are not functions
available in the actual scheme, but rather to the challenger in the experiments
we use to formalize security of \UAS schemes. We introduce them here, and define
them later for our construction.

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\upk,\usk,\sCred=
  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]},
  \Cred=(\cid,\attrs,\cred))$.]
  Receives trapdoor \trap and a valid $\langle \Obtain, \Issue \rangle$
  transcript \utrans. It outputs the credential \Cred issued as a result of the
  interaction in \utrans, along with the involved user key pair $(\upk,\usk)$
  and, if any, the credential set \sCred used to request \Cred.
\item[$\ExtractSign(\trap,\Sig) \rightarrow
  (\upk,\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives trapdoor \trap and a valid
  signature \Sig. It outputs the user secret key and credential set \sCred used
  to generate the signature, and the $\yeval^1$ and \yinsp values. 
% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
%   $0$.

@@

%   The \IdentifySig function defined by \UAS constructions must satisfy that, for
%   signatures accepted by \Verify, there must exist \emph{exactly one} $(\usk,
%   \scred)$ combination that makes \IdentifySig return $1$.
%   % . This is trivial for honest users, for which there must be a one-to-one
%   % relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
%   % to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
%   % to \uid, extract the used secret key, and check if there is a match. In the
%   % latter case, there is no guarantee of getting a one-to-one relationship
%   % between \usk and \uid. Also, when used for corrupt users, this can only be
%   % used when the issuer is honest, as transcripts are needed. 
\end{description}

@@

We thus extend unforgeability of signatures with issuance unforgeability,
\ExpForgeIssue. It captures that all honestly issued credentials meet the
requirements set by the corresponding issuer, and that any further credential
involved in the request is bound to the same known user. For this, we allow the
adversary \adv~to interact with the oracles (restricted to honest issuers).
Eventually, \adv~is challenged to output a credential identifier from which we
extract the actual witnesses used in the credential request associated to \cid.
\adv~wins if the issuance function, applied to the extracted values, does not
meet the expected output, or if not all of the credentials (if any) used to
support the request belong to the same (known) user to whom the new credential
was issued. Note that the issuance transcript associated to \cid must exist, as
we unavoidably need to restrict to honest issuers. Indeed, a dishonest issuer
cannot be trusted to enforce any policy, nor to properly keep all transcripts.

@@

In this section, we give a generic construction of an \UAS scheme, based on
generic building blocks. We use three different NP relations: \RelIss, \RelSig,
and \RelIns, described next and specified in CS notation \cite{cs97} in
\figref{fig:nizkrels}. Crucially, these relations include verifying that the
comptuation of the \fissue, \feval and \finsp functions has been done correctly.

@@

\paragraph{$\ipk \gets \ISet((\upk,\usk),\fissue)$.} %
A user willing to become an issuer just sets $\ipk \gets (\upk,\fissue)$, and
publishes \ipk. We assume that {\ipk}s are published in some properly (probably
authenticated) way.

@@

We state the correctness and security theorems next, and defer the proofs to
\appref{app:uas-proofs}.

@@

\begin{theorem}[Issuance unforgeability of \CUASGen]
  \label{thm:issue-forge-uas}  
  If the underlying NIZK used for \RelIss is simulation extractable, and the
  underlying \SBCM scheme is correct, then our \CUASGen construction satisfies
  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
\end{theorem}

@@

\paragraph{\CUASGenInt: Interactive Credential Presentations with replay
  protection.}
%
In group signatures, signing and verification are non-interactive processes;
whereas in anonymous credentials, they are an interactive protocol. \CUASGen
targets the non-interactive approach. Now, we sketch how to transform this into
an interactive protocol with replay protection.

>>>>

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all other functions.
\item[$\KeyGen(\parm) \rightarrow (% \Ccom,r,
  \upk,\usk)$.] Given \parm, a user
  runs \KeyGen to generate its user key pair% , and a commitment \Ccom to the
  % public key, with randomness $r$
  . 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and
  function \finsp, an opener runs \OKeyGen to generate its key pair. \finsp
  defines the utility extractable from signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\ipk,\sCred,\attrs),
  \Issue(\isk,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk receive a credential
  $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue function defined by the issuer, and $\utrans=(U,I)$ being the
  transcript of the communication% , where $U$ contains the messages sent by
  % the user, and $I$ those sent by the issuer
  .
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving user secret key \usk, opener public key \opk, 
  credentials \sCred, message \msg and evaluation function \feval, returns
  signature \sig, and a value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Run by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials by issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
These are the functional placeholders that allow modulating the behaviour of the
resulting instantiation. They control the conditions for issuing new
credentials, the information revealed alongside signatures, or extractable
from them. In all cases, the user computes them, and proves correctness of
such computation. We give concrete examples in \secref{sec:relationships}.

@@

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  honest {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  corrupt {\uid}s/{\iid}s/{\oid}s.
\item[\UK,\IK,\OK.] Tables storing key pairs of users $(\upk,\usk)$, issuers
  $(\ipk,\isk)$, and openers $(\opk,\osk)$, indexable by \uid, \iid, and \oid,
  respectively. Issuers' public keys contain a \fissue function, and
  openers' public keys contain a \finsp function.
\item[\PUBUK,\PUBIK,\PUBOK and \PRVUK,\PRVIK,\PRVOK.] Shorthands referring to
  public keys of users, issuers or openers ($\mathsf{PXK}$) or their private
  keys ($\mathsf{SXK}$).
\item[\CRED.] Indexable by \cid, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$) to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but tracks challenge credentials.
\item[\OWNR.] When we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
  $\bot$ if there is no such \uid. We also use \OWNR over a set of {\cid}s
  (\scid). In that case, $\OWNR[\scid]$ returns $\bot$ if
  not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
  \uid, all conditions checking membership of the output of \OWNR to a list of
  users equal false if \OWNR returns $\bot$.
\item[\ATTR.] When we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] When we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Stores challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

\paragraph{Oracles.} %
We leverage the following oracles, formalized in \figref{fig:oracles1} and
\figref{fig:oracles2}.

\begin{description}
% \item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
%   the associated issuance function.
\item[\HUGEN.] Adds a new honest user, generating its keypair.
\item[\CUGEN.] Adds a new corrupt user. Sets its \upk to the
  one given by the adversary.  
\item[\OGEN.] Adds a new opener, generates its key pair and sets its opening
  function.
% \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
%   key to the adversary.
\item[\ISET.] ``Upgrades'' a user to become an issuer, specifying its
  \fissue function.
\item[\UCORR.] Corrupts an existing honest user, giving its \usk to the
  adversary. If the user was also an issuer, it becomes a corrupt issuer too.
\item[\OCORR.] Corrupts an existing honest opener, giving its \osk to the
  adversary.
% \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
%   the user's key pair.
% \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
%   user already exists and is honest, corrupts it, leaking its key and
%   credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures using credentials from honest
  users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

@@

    \caption{Detailed oracles available in our model (1/2). Oracles for
      key generation.}
    \label{fig:oracles1}
  \end{figure*}
}

@@

      \begin{minipage}[t]{.55\textwidth}

@@

\paragraph{Helper functions % \SimSetup, \ExtractIssue, and \ExtractSign
  .}
We assume the existence of these helper functions. They are not functions
available in the actual scheme, but rather to the challenger in the experiments
we use to formalize security of \UAS schemes. We introduce them here, and define
them later for our construction.

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\upk,\usk,\sCred=
  \lbrace(\cid_i,\attrs_i,\cred_i,\ipk_i) \rbrace_{i \in [n]},
  \Cred=(\cid,\attrs,\cred,\ipk))$.]
  Receives trapdoor \trap and a valid $\langle \Obtain, \Issue \rangle$
  transcript \utrans. It outputs the credential \Cred issued as a result of the
  interaction in \utrans, along with the involved user key pair $(\upk,\usk)$
  and the credential set \sCred used to request \Cred, of size $n$, where $n$
  may be $0$.
\item[$\ExtractSign(\trap,\Sig) \rightarrow
  (\upk,\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives trapdoor \trap and a valid
  signature \Sig. It outputs the user secret key and credential set \sCred used
  to generate the signature, and the $\yeval^1$ and \yinsp values. 
% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
%   $0$.

@@

%   The \IdentifySig function defined by \UAS constructions must satisfy that, for
%   signatures accepted by \Verify, there must exist \emph{exactly one} $(\usk,
%   \scred)$ combination that makes \IdentifySig return $1$.
%   % . This is trivial for honest users, for which there must be a one-to-one
%   % relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
%   % to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
%   % to \uid, extract the used secret key, and check if there is a match. In the
%   % latter case, there is no guarantee of getting a one-to-one relationship
%   % between \usk and \uid. Also, when used for corrupt users, this can only be
%   % used when the issuer is honest, as transcripts are needed.
\item[$\VerCred(\usk,\cid,\attrs,\cred,\ipk) \rightarrow 1/0$.] Returns
  $1$ if \cred is a valid credential with identifier \cid, issued by an issuer
  with public key \ipk, over attributes \attrs, and bound to user secret key
  \usk. Otherwise, it returns $0$.
\end{description}

@@

We thus extend unforgeability of signatures with issuance unforgeability,
\ExpForgeIssue. It captures that all honestly issued credentials meet the
requirements set by the corresponding issuer, and that any further credential
involved in the request is a valid credential, bound to the same known user. For
this, we allow the adversary \adv~to interact with the oracles (restricted to
honest issuers). Eventually, \adv~is challenged to output a credential \Cred
from which we extract the actual witnesses used in the credential request
associated to \cid. \adv~wins if the issuance function, applied to the extracted
values, does not meet the expected output, if not all of the credentials (if
any) used to endorse the request belong to the same (known) user to whom the new
credential was issued, or if any of such credentials is a forgery. Note that the
issuance transcript associated to the credential output by the adversary must
exist, as we unavoidably need to restrict to honest issuers. Indeed, a dishonest
issuer cannot be trusted to enforce any policy, nor to properly keep all
transcripts.

@@

We give a generic construction of an \UAS scheme, based on
generic building blocks. We use three different NP relations: \RelIss, \RelSig,
and \RelIns, described next and specified in CS notation \cite{cs97} in
\figref{fig:nizkrels}. These relations include verifying that the comptuation of
the \fissue, \feval and \finsp functions has been done correctly.

@@

\paragraph{$\ipk \gets \ISet((\upk,\usk),\fissue)$.} %
A user willing to become an issuer just sets $\ipk \gets (\upk,\fissue)$, and
publishes \ipk. We assume that {\ipk}s are published in some proper (probably
authenticated) way.

@@

We now state the correctness and security theorems, and defer the proofs to
\appref{app:uas-proofs}.

@@

\begin{theorem}[Issuance unforgeability of \CUASGen]
  \label{thm:issue-forge-uas}  
  If the underlying NIZK used for \RelIss is simulation extractable, and the
  underlying \SBCM scheme is correct and one-more unforgeable, then our \CUASGen
  construction satisfies issuance unforgeability as defined in
  \defref{def:issue-forge-uas}.
\end{theorem}

@@

\paragraph{\CUASGenInt: Interactive Credential Presentations with replay
  protection.}
%
In group signatures, signing and verification are non-interactive processes;
whereas in anonymous credentials, it is an interactive protocol. While
\CUASGen targets the non-interactive approach, we sketch how to transform it
into an interactive protocol with replay protection.

### 2022-10-04 prism-backend/research/gsac/introduction-paper.tex
30 pages.

%% Brief description of main precedents (simple words)
\paragraph{Anonymous authentication and signatures.} %
Privacy-preserving signature and authentication systems have been a prolific
field in the last decades. Anonymous credentials (AC) \cite{chau85} and group
signatures (GS) \cite{ch91} are among the most relevant schemes. In both, the
high-level idea is common: users obtain credentials, which can then use to
authenticate anonymously and indistinguishably from other users with similar
credentials. 
%
%% Usefulness of main precedents / motivation
Their usefulness stems from the combination of seemingly contradictory concepts:
anonymity, authentication, and utility; where utility can appear in the shape of
information revealed at signature/authentication time, or after (in the latter
case, typically called accountability).

@@

%% Previous works summary w/ refs directly related contribs of UAS
%% (or, tech approaches of main precedents)
\paragraph{Evolution of AC and GS.} %
AC and GS systems have followed separate paths, with some exceptions.
Functionality-wise, Attribute-Based Group Signatures add attributes to the
credentials issued to group members, who can later use them to prove pre-fixed
claims \cite{emo09,aa14}. Hidden identity-based signatures also add attributes
to the credentials, with the aim of preventing the opener (the trusted party who
can deanonymize signers) from having to rely on the issuer in order to return
meaningful identifying information when opening a signature \cite{ks07}. Some AC
schemes also incorporate some sort of utility after authentication, like
AC schemes with revocation \cite{cks10}.

@@

%% Main drawbacks of precedents
\paragraph{Limitations of GS and AC.} %
However, even the generalisation efforts that have independently taken place in
GS and AC have limited applicability in the real world. On the GS side, even
though MPS achieves a powerful balance on when a signature is
deanonymizable and what information can be extracted from it, upon closer look,
this information is somehow meaningless. Namely, the notion of identity is not
well defined and, thus, it is not possible to assess whether the value output by
their generalised open function makes sense or even if it is legitimate. Also,
just being able to prove membership at signing time is typically not enough. In
other words, in GS, utility at authentication time is very limited -- but this
is precisely the main strength in AC schemes, which also have a well defined
notion of identity via attributes. On the other hand, the notion of
accountability  is barely present in AC schemes. For instance, non-frameability
is not even considered, and it is non-frameability what prevents honest users
from being held accountable of dishonest actions they did not take part in.
%
In any case, perhaps the most impractical limitation of all is that too many
models exist in both fields. Although similar, each model focuses on slightly
different utility variants, making them hardly comparable. To the best of our
knowledge, no model exists that combines both fields, in a general enough
manner. In practice, needing to resort to too specific models forces system
designers to decide which feature they do not want to lose -- or, which one they
will lose.

>>>>

%% Brief description of main precedents (simple words)
\paragraph{Anonymous authentication and signatures.} %
Privacy-preserving signature and authentication systems have been a prolific
field for decades. Anonymous credentials (AC) \cite{chau85} and group signatures
(GS) \cite{ch91} are among the most relevant schemes. In both, the
high-level idea is common: users obtain credentials, which can then use to
authenticate anonymously and indistinguishably from other users with similar
credentials. 
%
%% Usefulness of main precedents / motivation
Their usefulness stems from the combination of seemingly contradictory concepts:
anonymity, authentication, and utility; where utility can appear in the shape of
information revealed at signature/authentication time, or after (in the latter
case, typically called accountability).

@@

%% Previous works summary w/ refs directly related contribs of UAS
%% (or, tech approaches of main precedents)
\paragraph{Evolution of AC and GS.} %
AC and GS systems have followed separate paths, with exceptions.
Functionality-wise, Attribute-Based Group Signatures add attributes to the
credentials issued to group members, who can later use them to prove fixed
claims \cite{emo09,aa14}. Hidden identity-based signatures also add attributes
to the credentials, to prevent the opener (the trusted party who
can deanonymize signers) from having to rely on the issuer in order to return
meaningful identifying information when opening a signature \cite{ks07}. Some AC
schemes also incorporate some utility after authentication, like
revocable AC schemes \cite{cks10}.

@@

%% Main drawbacks of precedents
\paragraph{Limitations of GS and AC.} %
Even the independent generalisation efforts in both GS and AC
have limited applicability in the real world. On the GS side, although MPS
achieves a powerful balance on when a signature is deanonymizable and what
information can be extracted, upon closer look, this information is somehow
meaningless. Namely, the notion of identity is not well defined and, thus, it is
not possible to assess whether the value output by their generalised open
function makes sense or even if it is legitimate. Also, proving membership at
signing time is typically not enough. In other words, in GS,
utility at authentication time is very limited. This is precisely the main
strength in AC schemes, which also have a well defined notion of identity via
attributes. Conversely, the notion of accountability  is barely present in AC
schemes. For instance, non-frameability is not even considered, and it is
non-frameability what prevents honest users from being held accountable of
dishonest actions they did not take part in.
%
In any case, perhaps the most impractical limitation of all is that too many
models exist in both fields. Although similar, each model focuses on slightly
different utility variants, making them hardly comparable. To the best of our
knowledge, no model exists that combines both fields, in a general enough
manner. In practice, needing to resort to too specific models forces system
designers to decide which feature they do not want to lose -- or, which one they
will lose.
